TUD Datasets: A collection of benchmark datasets for learning with graphs

### 2020-03-26 main.tex
MC.

\paragraph{Contributions} We give an overivew of \textsc{Tud dataset}.

>>>>

\paragraph{Contributions} We give an overview of \textsc{Tud dataset}, its unified evalution procudures, and baseline methods. Moreover, we report results on a experimental study comparing graph kernels and GNNs on a subset of the \textsc{Tud dataset}.
